On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 preliminaries.tex
Change thm env
Use right env for def proto ind-cpa

\hannote{original text?}
\begin{theorem}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$.
	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda(H_2|_{K^\bot})}$$
	$$\lambda(H_1+JH_2)\geq\lambda(H_1\big|_K)-\frac{1}{8}$$
\end{theorem}

@@

There are many formulations of quantum de Finetti theorems. We use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
\begin{theorem}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
\end{theorem}

@@

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{I think this point is obvious?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}

@@

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{algorithmic}[1]
		\State The challenge picks $b\in\set{0,1}$ at random
		\If{$b=1$}
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\Else
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\EndIf
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}

>>>>

\hannote{original text?}
\begin{thm}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$.
	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda(H_2|_{K^\bot})}$$
	$$\lambda(H_1+JH_2)\geq\lambda(H_1\big|_K)-\frac{1}{8}$$
\end{thm}

@@

There are many formulations of quantum de Finetti theorems. We use the one from \cite{Brandão2017} because we need logarithmic dependence on $|A|$.
\begin{thm}
	\label{deFinetti}
	Let $\rho^{A_1\ldots A_k}$ be a permutation-invariant state. Then for every $0\leq l\leq k$ there exists states $\set{\rho_i}$ and $\set{p_i}\subset\bbR$ such that
	$$\max_{\Lambda_1,\ldots,\Lambda_l}\norm{(\Lambda_1\otimes\ldots\otimes\Lambda_l)\left(\rho^{A_1\ldots A_l}-\sum_ip_i\rho_i^{A_1}\otimes\ldots\otimes\rho_i^{A_l}\right)}_1\leq\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$$
\end{thm}

@@

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}

@@

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{enumerate}
		\item The challenge picks $b\in\set{0,1}$ at random
		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\item $\cA$ attempts to guess $b$
	\end{enumerate}
\end{protocol}
